%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Guanhua Chen} % Your name
\address{520 S Lasalle st, \\ Durham, NC} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{(984)~$\cdot$~245~$\cdot$~5931 \\ guanhua.chen@duke.edu} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf DUKE University} \hfill {\em August 2019 - Present} \\ 
M.S. in Electrical \& Computer Engineering \\
GPA: 3.57/4.0

{\bf Huazhong University of Science and Technology } \hfill {\em September 2015 - June 2019} \\ 
B.S. in Electrical \& Computer Engineering \\
GPA: 3.75/4.0
\end{rSection}

%----------------------------------------------------------------------------------------
%	COURSE PROJECTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Course Projects}
    \begin{rSubsection}{Sally Stash}{January 2020 - February 2020}
        {Individual project: Java}
        {Durham, NC}
        \item Developed a full stack web application let users request, drive for and join rides.
        \item Built user friendly interface at the front-end using Bootstrap, CSS and JavaScript.
        \item Used PostgreSQL to store user data at the back-end.
        \end{rSubsection}
    \begin{rSubsection}{Ride Sharing Service}{December 2019 - January 2020}
        {Individual project: Django, PostgreSQL, Bootstrap}
        {Durham, NC}
        \item Developed a full stack web application let users request, drive for and join rides.
        \item Built user friendly interface at the front-end using Bootstrap, CSS and JavaScript.
        \item Used PostgreSQL to store user data at the back-end.
        \end{rSubsection}

    \begin{rSubsection}{Command Shell}{November 2019 - December 2019}
    {Individual project: Linux, C++}
    {Durham, NC}
    \item Tokenized the input string and handled the complex combination of symbol \textbackslash, ", \$ and white space.
    \item Searched the PATH environment variable for commands, then forked and executed.
    \item Provided access to variable. User could set, export and reverse the variable.
    \item Added redirection function for input, output and error output.
    \end{rSubsection}

%------------------------------------------------

    \begin{rSubsection}{Huffman compressor}{October 2019 - November 2019}
    {Individual project: C++}
    {Durham, NC}
    \item Designed a file compressor based on Huffman coding.
    \item Constructed a priority queue based on the word frequency, then built a binary tree.
    \item Used the binary tree to create a map which encoded characters with the appropriate bit strings.
    \end{rSubsection}


\end{rSection}

%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	RESEARCH SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Research Experience}

    \begin{rSubsection}{Mid-infrared Tunable Lasers}{November 2017 - December 2018}
    {Research asassistant: MATLAB}
    {Wuhan, China}
    \item Designed a tunable optical parametric oscillator for generating mid-infrared lasers.
    \item Conducted numerical simulation with MATLAB and helped build up the oscillator.
    \item The new system generated superior quality beam and the result was published on Optics Letter.
    \end{rSubsection}
    
\end{rSection}

%----------------------------------------------------------------------------------------
%	COURSES
%----------------------------------------------------------------------------------------

\begin{rSection}{Courses}

\item Object-Oriented Programming, Data Structure and Algorithm, Operating System, Computer Network, Database

\end{rSection}

%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages & C++, C, Python, Java, SQL, MATLAB \\
%%Protocols \& APIs & XML, JSON, SOAP, REST \\
%Databases & MySQL, PostgreSQL, Microsoft SQL \\
Tools & Emacs, GDB, Valgrind, Django, PostgreSQL, Bootstrap
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
